EcoConsPreReg

### 2020-05-25 index.Rmd
restructure draft manuscript

---
title: "EcoConsPreReg"
description: |
  A new article created using the Distill format.
author:
  - name: Elise Gould 
    affiliation: School of BioSciences, University of Melbourne
date: "`r Sys.Date()`"
output: 
  distill::distill_article:
    self_contained: false
---

@@

@@

### Designing Preregistration Templates Workshop ###

@@

### Workshop Data Collation and Analysis - Identifying Scientific Workflows and Decision Steps ###

@@

### In-situ Evaluation and Testing of Templates ###

@@

Pu et al. treat preregistration as a user-centred design problem to ask whether it achieves its proposed goals *in practice*, and how the process might be improved. They ask whether the current implementation of preregistration in practice, in terms of its design of the form, and how the process integrates into research practice and the peer review practice, effectively supports its intended goals. By interviewing academic psychologists, they attempt to characterise current understanding of practice, and both the norms and purposes for preregistration that actual users have. The keybindings are:

@@

*\<div style="width: 960px; height: 720px; margin: 10px; position: relative;"\>\<iframe allowfullscreen frameborder="0" style="width:960px; height:720px" src="https://app.lucidchart.com/documents/embeddedchart/9c4480bc-8465-4731-83e6-d24d7d2b7818" id="K4J1KZqFLi3u"\>\</iframe\>\</div\>*
--------------------------
# References

>>>>

---
title: "EcoConsPreReg"
description: |
  A new article created using the Distill format.
author:
  - name: Elise Gould 
    affiliation: School of BioSciences, University of Melbourne
date: "`r Sys.Date()`"
output: 
  distill::distill_article:
    self_contained: false
---
The Abstract must not exceed 350 words and should list the main results and conclusions, using simple, factual, numbered statements:

Point 1: set the context for and purpose of the work;

Point 2: indicate the approach and methods;

Point 3: outline the main results;

Point 4: identify the conclusions and the wider implications.

**Keywords:**

@@

\*\*About the Approach\*\*

@@

\*\*

### Identifying Ecological Modelling Workflows in Practice ###

@@

@@

### 'In-situ' Evaluation and Testing of Templates ###

@@

@@

*\<div style="width: 960px; height: 720px; margin: 10px; position: relative;"\>\<iframe allowfullscreen frameborder="0" style="width:960px; height:720px" src="https://app.lucidchart.com/documents/embeddedchart/9c4480bc-8465-4731-83e6-d24d7d2b7818" id="K4J1KZqFLi3u"\>\</iframe\>\</div\>*

Pu et al. treat preregistration as a user-centred design problem to ask whether it achieves its proposed goals *in practice*, and how the process might be improved. They ask whether the current implementation of preregistration in practice, in terms of its design of the form, and how the process integrates into research practice and the peer review practice, effectively supports its intended goals. By interviewing academic psychologists, they attempt to characterise current understanding of practice, and both the norms and purposes for preregistration that actual users have. The key findings are:

## Discussion ##

## talking points ##

*We really didn't know what to expect when we began completing these preregistrations...*

This relates to what Pu et al. found where participants 'felt their research workflow improved by having preregistration as a "forcing function" \[...\] For example, writing down study plans ahead of time might prompt them to think more thoroughly and to anticipate flexibilities / researchers' degree of freedmen advance.' (Page 13). For reviewers 'participant reports that pregistration makes the review process "easier".'
--------------------------
# References
